Nondeterministic Bigraphical Reactive Systems for Markov Decision Processes\thanks{Supported by an EPSRC Vacation Scholarship.}

### 2018-08-16 paper.tex
Agent 1 part of PRISM

\documentclass[runningheads]{llncs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{color}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{wasysym}
\usepackage[lighttt]{lmodern}
\usepackage{siunitx}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{phaistos}
\usepackage{subcaption}

@@

\title{Nondeterministic Bigraphical Reactive Systems for Markov Decision
  Processes\thanks{Supported by organization x.}}
\titlerunning{Nondeterministic BRSs for MDPs}
\author{Paulius Dilkas}
\authorrunning{P. Dilkas}
\institute{University of Glasgow, Glasgow, UK}
\maketitle

@@

@@

TODO (possibly): state transition diagrams and statistics about the number of
states, etc.
TODO: quantitative analysis with PRISM (need good nontrivial examples)

>>>>

\documentclass[runningheads]{llncs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{color}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{wasysym}
\usepackage[lighttt]{lmodern}
\usepackage{siunitx}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{phaistos}
\usepackage{subcaption}
\usepackage{booktabs}

@@

\title{Nondeterministic Bigraphical Reactive Systems for Markov Decision
  Processes\thanks{Supported by an EPSRC Vacation Scholarship.}}
\titlerunning{Nondeterministic BRSs for MDPs}
\author{Paulius Dilkas}
\authorrunning{P. Dilkas}
\institute{University of Glasgow, Glasgow, UK}
\maketitle

@@

\subsection{Exporting to PRISM}

% TODO: need to cite something about the syntax, logic, etc.
Now that we have two models defined in BigraphER, we will briefly show how they
can be exported and used for quantitative analysis with PRISM.

For our first model, we set the probability of finding an object to $p = 0.5$
and keep the same $2 \times 2$ grid. We ask PRISM to compute \texttt{Pmax=? [ F
  "goal" ]}, i.e., the maximum probability of reaching the goal. Recall that the
goal is to collect $n$ objects. We vary $n$ from $1$ to $3$ (as collecting $0$
objects is trivial, and collecting more than $3$ is impossible given the size of
the grid) and show the resulting probabilities in Table \ref{agent1_prism}. The
reader is welcome to check that the numbers are as expected.

\begin{table}
  \centering
  \begin{tabular}{l r r r}
    \toprule
    $n$ & \tablenum{1} & \tablenum{2} & \tablenum{3} \\
    \texttt{Pmax} & \tablenum{0.875} & \tablenum{0.5} & \tablenum{0.125} \\
    \bottomrule
  \end{tabular}
  \caption{The maximum probability of collecting $n$ objects in a $2 \times 2$
    grid, where the probability of finding an object is \num{0.5} when visiting
    a cell for the first time.}
  \label{agent1_prism}
\end{table}

For the second model..

@@

TODO (possibly): state transition diagrams and statistics about the number of
states, etc.
